---
title: "execute"
author: "anonymous"
output: pdf_document
---

This Rmd is generating 50 synthetic data sets (of same size as the real data) from a C-vine for truncation levels 1, 5, 10, 15, 20 and 26 (which is equal to no truncation) using the real-world SUPPORT2 data set. The function used to generate synthetic data from a C-vine is called "generate_synth_data.R". Then these synthetic data are evaluated in terms of utility using the function defined in "evluate_synth_data_testdata.R". Using the privacy attack code by Stadler et. al. in the repository "synthetic_data_release", the privacy of the synthetic data are evaluated and the results plotted here.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)

library(readr)
library(dplyr)
library(rvinecopulib)
library(data.table)
library(pROC)
library(ggplot2)
library(doBy)
library(tidyr)
library(latex2exp)
library(randomForest)
library(cowplot)
library(RColorBrewer)
library(stringr)

```

## Loading Data and Functions

```{r}
# function to generate synthetic data "generate_synth_data_all_truncs":
source("./src/generate_synth_data.R")

# function to evaluate synthetic data in terms of utility "evaluate_synth_data_testdata":
source("./src/evaluate_synth_data_testdata.R")

# function for rearranging utility results "making_tables":
source("./src/making_tables.R")

# reading real and test data
real_data <- read.csv("./data/preprocessed/real_support2_small.csv")
test_data <- read.csv("./data/preprocessed/test_support2_small.csv")
```


## Preparing Real Data and Defining Covariate Ordering

```{r}
n <- dim(real_data)[1]
d <- dim(real_data)[2]

# no. synthetic data sets of size n generated per model
p_synth <- 50

trunc_levels <- c(1, seq(5,20,5), 26)
factor_position <- c(d)
vine_estimation <- "par"


attribute_names <- colnames(real_data)

# preparing real data and test data
real_data$Y <- real_data$Y %>% as.factor()
real_data <- as.data.table(real_data)

test_data$Y <- test_data$Y %>% as.factor()
test_data <- as.data.table(test_data)
```

# UTILITY
## Benchmark: Utility of the Same Classifier Trained on Real Data

```{r}
set.seed(456)
data <- as.data.frame(real_data)
data$Y <- data$Y %>% as.factor()

t_data <- as.data.frame(test_data)
t_data$Y <- t_data$Y %>% as.factor()

rf.err.rate <- function(x){
  fit <- randomForest(Y ~ ., data = data, ntree = x, mtry = floor(sqrt(d - 1)), replace = T, type = "classification")
  y <- mean(fit$err.rate[,1])
  return(y)
}

obb.err.mean <- vapply(X = seq(from=100, to=2000, by=100), FUN = rf.err.rate, numeric(1))
ntrees.opt <- seq(from=100, to=2000, by=100)[which(min(unlist(obb.err.mean)) == unlist(obb.err.mean))]


rf.model <- randomForest(Y ~ ., data = data, ntree = ntrees.opt, 
                         mtry = floor(sqrt(d - 1)), nodesize = 1, replace = T, type = "classification")
predictions <- predict(rf.model, newdata = t_data[, -d], type = "response", 
                       norm.votes = T) %>% as.numeric()

AUCreal <- auc(response = t_data$Y, predictor = as.numeric(predictions)- 1)
print("AUC:"); AUCreal
```


## Generating Synthetic Data for Specified Truncation Levels from a C-vine

```{r}
set.seed(456)
list_synth_data <- generate_synth_data_all_truncs(real_data, p_synth, attribute_names, factor_position, vine_estimation, vine_topology = "Cvine", trunc_levels = trunc_levels)

rm(factor_position, vine_estimation, attribute_names)
```


## Evaluating the Utility of C-vine Generated Synthetic Data with a Random Forest Classifier

```{r, echo = F}
set.seed(4562)
utility_per_trunc <- list()
for (t in 1:length(list_synth_data)){
  utility_per_trunc[[t]] <- evaluate_synth_data_testdata(real_data, list_synth_data[[t]], test_data, p_synth, classifier = "rand_forest")
  names(utility_per_trunc)[t] <- names(list_synth_data)[t]
}

names(utility_per_trunc) <- names(list_synth_data)

saveRDS(utility_per_trunc, file = "./output/utility_realsupport2_small_Cvine_randForest_p50_testdata.RData")
# utility_per_trunc <- readRDS("./output/utility_realsupport2_small_Cvine_randForest_p50_testdata.RData")
```


## Rearranging Utility Results of C-Vine Generated Synthetic Data
```{r}
modelname <- "Cvine"
names(utility_per_trunc) <- paste0(modelname, "_trunc_", names(utility_per_trunc))
resultsCvine <- making_tables(utility_per_trunc, as_matrix = T)
models <- colnames(resultsCvine)
cnames <- row.names(resultsCvine)
resultsCvine <- t(resultsCvine)
colnames(resultsCvine) <- cnames
row.names(resultsCvine) <- NULL
resultsCvine <- resultsCvine %>% as.data.frame()
resultsCvine$model <- models

rm(models, cnames)

resultsCvine <- resultsCvine %>% separate(model, into = c("model", "t", "trunc"), sep = "_")
resultsCvine$t <- NULL
resultsCvine[, c("model", "trunc")] <- lapply(resultsCvine[, c("model", "trunc")], factor)

subdf <- resultsCvine[resultsCvine$model == "Cvine",]
med <- summaryBy(AUC_synth ~ (trunc), data = subdf, FUN = list(median)) %>% as.data.frame()
```


## Plotting Utility Results Cvine

```{r, warning = F}

gCvine <- ggplot(subdf, aes(x = trunc, y = AUC_synth)) +
  geom_boxplot(width = 0.4, linewidth = 1.5, position=position_dodge(0.6), fill = '#0099FF') +
  labs(x ="truncation level", y = TeX(r'($AUC(y^*, \hat{w}^*)$)')) +
  theme_minimal() +
  theme(text = element_text(size = 30), legend.position = "bottom",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = element_text(size=30),
        axis.text.y = element_text(size=30),
        legend.text = element_text(size = 40),
        plot.margin=unit(c(2,0,0.5,0.5), 'cm')) +
  scale_y_continuous(breaks = seq(from = 0.5, to = 0.8, by = 0.1), limits = c(0.45, 0.8)) +
  geom_path(data = med, aes(x = trunc, y = AUC_synth.median), color = '#0099FF', group=1, size = 2) +
  scale_x_discrete(labels = c(paste(unique(subdf$trunc)[-length(unique(subdf$trunc))]), 'no')) +
  geom_hline(yintercept=AUCreal, alpha = 0.8, color = '#FF6633', size=2) +
  geom_text(x = 1.5, y = (AUCreal+0.07), label = TeX(r'($AUC(y^*, \hat{y}^*)$)'), size = 10, color = '#FF6633') +
  panel_border()

gCvine
```


## Evaluating the Utility of PrivBayes Generated Synthetic Data with a Random Forest Classifier

```{r, echo = F}
synth_data_competitors <- list()

# reading in PrivBayes synthetic data generated beforehand in python
for (i in 1:3){
  synth_data <- read.csv(paste0("./data/synthdata_utility_competitors/synth_data_PrivBayes", c("01", "1", "5")[i], "_real_support2_small.csv"))
  synth_data$Y <- synth_data$Y %>% as.factor()
  synth_data_competitors[[i]] <- synth_data
}

names(synth_data_competitors) <- paste("PrivBayes_", c("01", "1", "5"), sep = "")

# evaluating utility with random forest classifier
set.seed(472)
util_competitors <- list()
for (i in 1:length(synth_data_competitors)){
  util_competitors[[i]] <- evaluate_synth_data_testdata(real_data, synth_data_competitors[[i]], test_data, p_synth, classifier = "rand_forest")
}

names(util_competitors) <- names(synth_data_competitors)

# saving results
saveRDS(util_competitors, file = "./output/utility_realsupport2_small_PrivaBayes_eps_01_1_5_randForest_p50_testdata.RData")
# util_competitors <- readRDS("./output/utility_realsupport2_small_PrivaBayes_eps_01_1_5_randForest_p50_testdata.RData")


# rearranging results for plotting
resultsPrivBayes <- making_tables(util_competitors, as_matrix = T)
models <- colnames(resultsPrivBayes)
cnames <- row.names(resultsPrivBayes)
resultsPrivBayes <- t(resultsPrivBayes)
colnames(resultsPrivBayes) <- cnames
row.names(resultsPrivBayes) <- NULL
resultsPrivBayes <- resultsPrivBayes %>% as.data.frame()
resultsPrivBayes$model <- models

rm(models, cnames)


resultsPrivBayes <- resultsPrivBayes %>% separate(model, into = c("model", "eps"), sep = "_")
resultsPrivBayes$eps[resultsPrivBayes$eps == "01"] <- "0.1"
resultsPrivBayes[, c("model", "eps")] <- lapply(resultsPrivBayes[, c("model", "eps")], factor)

df <- subset(resultsPrivBayes, model == "PrivBayes")  
medPB <- summaryBy(AUC_synth ~ eps, data = df, FUN = list(median)) %>% as.data.frame()
```


## Plotting Utility Results PrivBayes

```{r, warning = F}

gPB <- ggplot(df, aes(x = eps, y = AUC_synth)) + 
  geom_boxplot(width = 0.4, linewidth = 1.5, position=position_dodge(0.6), fill = '#0099FF') +
  # scale_fill_manual(labels = c("PrivBayes"), values = c( '#FF6633')) +
  labs(x =TeX(r'($\epsilon$)'), y = "") + # TeX(r'($AUC(y^*, \hat{w}^*)$)')
  theme_minimal() +
  theme(text = element_text(size = 40), legend.position = "bottom",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = element_text(size=30),
        axis.text.y = element_blank(),
        legend.text = element_text(size = 40),
        plot.margin=unit(c(2,0.5,0.5,-1), 'cm')) +
  geom_path(data = medPB, aes(x = eps, y = AUC_synth.median), color = '#0099FF', group=1, size = 2) +
  scale_y_continuous(breaks = seq(from = 0.5, to = 0.8, by = 0.1), limits = c(0.45, 0.8)) +
  geom_hline(yintercept=AUCreal, alpha = 0.8, color = "#FF6633", size=2) +
  panel_border()

gPB
```


## Evaluating the Utility of CTGAN and TVAE Generated Synthetic Data with a Random Forest Classifier

```{r, echo = F}
# reading in synthetic data generated beforehand in python
synth_data_ctgan <- read.csv("./data/synthdata_utility_competitors/synth_data_CTGAN_real_support2_small.csv")
synth_data_tvae <- read.csv("./data/synthdata_utility_competitors/synth_data_TVAE_real_support2_small.csv")

synth_data_ctgan$Y <- synth_data_ctgan$Y %>% as.factor()
synth_data_tvae$Y <- synth_data_tvae$Y %>% as.factor()

synth_data_competitors <- list("CTGAN" = synth_data_ctgan, "TVAE" = synth_data_tvae)

# evaluating utility with random forest classifier
set.seed(123)
util_competitors <- list()
for (i in 1:length(synth_data_competitors)){
  util_competitors[[i]] <- evaluate_synth_data_testdata(real_data, synth_data_competitors[[i]], test_data, p_synth, classifier = "rand_forest")
}

names(util_competitors) <- names(synth_data_competitors)

# saving results
saveRDS(util_competitors, file = "./output/utility_realsupport2_small_CTGAN_TVAE_randForest_p50_testdata.RData")
# util_competitors <- readRDS("./output/utility_realsupport2_small_CTGAN_TVAE_randForest_p50_testdata.RData")
utilityCT <- util_competitors



# rearranging results for plotting
resultsCT <- making_tables(utilityCT, as_matrix = T)
models <- colnames(resultsCT)
cnames <- row.names(resultsCT)
resultsCT <- t(resultsCT)
colnames(resultsCT) <- cnames
row.names(resultsCT) <- NULL
resultsCT <- resultsCT %>% as.data.frame()
resultsCT$model <- models

rm(models, cnames)
```


## Plotting Utility Results CTGAN and TVAE

```{r}

gCT <- ggplot(resultsCT, aes(x = model, y = AUC_synth)) + 
  geom_boxplot(width = 0.4, linewidth = 1.5, position=position_dodge(0.6), fill = '#0099FF') +
  labs(x ='', y = '') +
  theme_minimal() +
  theme(text = element_text(size = 40), legend.position = "bottom",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = element_text(size=20),
        axis.text.y = element_blank(),
        legend.text = element_text(size = 40),
        plot.margin=unit(c(2,0,0.5,-1), 'cm')) +
  scale_y_continuous(breaks = seq(from = 0.5, to = 0.8, by = 0.1), limits = c(0.45, 0.8)) +
  geom_hline(yintercept=AUCreal, alpha = 0.8, color = "#FF6633", size=2)  + # #990066
  panel_border()

gCT
```
## Evaluating the Utility of PrivPGD Generated Synthetic Data with a Random Forest Classifier

```{r, echo = F}
# reading in PrivPGD synthetic data generated beforehand in python
synth_data_privpgd <- read.csv("./data/synthdata_utility_competitors/synth_data_PrivPGD_real_support2_small.csv")

synth_data_privpgd$Y <- synth_data_privpgd$Y %>% as.factor()

# evaluating utility with random forest classifier
set.seed(123)
util_competitors <- evaluate_synth_data_testdata(real_data, synth_data_privpgd, test_data, p_synth, classifier = "rand_forest")


# saving results
saveRDS(util_competitors, file = "./output/utility_realsupport2_small_PrivPGD_randForest_p50_testdata.RData")
# util_competitors <- readRDS("./output/utility_realsupport2_small_PrivPGD_randForest_p50_testdata.RData")

util_competitors <- list("PrivPGD 2.5" = util_competitors)
utilityPrivpgd <- util_competitors


# rearranging results for plotting
resultsPrivpgd <- making_tables(utilityPrivpgd, as_matrix = T)
models <- colnames(resultsPrivpgd)
cnames <- row.names(resultsPrivpgd)
resultsPrivpgd <- t(resultsPrivpgd)
colnames(resultsPrivpgd) <- cnames
row.names(resultsPrivpgd) <- NULL
resultsPrivpgd <- resultsPrivpgd %>% as.data.frame()
resultsPrivpgd$model <- models

rm(models, cnames)
```


## Plotting Utility Results PrivPGD

```{r}

gPrivpgd <- ggplot(resultsPrivpgd, aes(x = model, y = AUC_synth)) + 
  geom_boxplot(width = 0.4, linewidth = 1.5, position=position_dodge(0.6), fill = '#0099FF') +
  labs(x ='', y = '') +
  theme_minimal() +
  theme(text = element_text(size = 40), legend.position = "bottom",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = element_text(size=20),
        axis.text.y = element_blank(),
        legend.text = element_text(size = 40),
        plot.margin=unit(c(2,0,0.5,-1), 'cm')) +
  scale_y_continuous(breaks = seq(from = 0.5, to = 0.8, by = 0.1), limits = c(0.45, 0.8)) +
  geom_hline(yintercept=resultsPrivpgd$AUC_real, alpha = 0.8, color = "#FF6633", size=2)  + # #990066
  panel_border()

gPrivpgd
```



## Putting Utility Plots Together

```{r, warning = F}
plot_grid(
  gCvine, gCT, gPrivpgd, gPB,
  labels = c("CVINE", "CTGAN  TVAE", "PrivPGD", "PrivBayes"),
  label_size = 40,
  hjust = 0,
  vjust = 1.3,
  ncol = 4,
  rel_widths = c(13, 4, 3, 5),
  label_x = c(0.48, 0.05, 0.15, 0.2, -0.5),  # Adjust these values to change label positions
  label_y = 1
)

name <- paste0("./figures/utility_realsupport2_small_CvinePrivBayesPrivpgdCTGANTVAE_randForest_AUC", ".png", sep = "")
ggsave(filename = name, width = 25, height = 5, units = "in", bg = "white", limitsize = F)
```


# PRIVACY
## Reading Attribute Inference Attack Results Produced in Python

```{r}
# sensitive attribute
sa <- "totcst"

before_trunc <- paste0("output/inference_realsupport2_small_", sa, "Outlier_trunc", sep = "")
after_trunc <- paste0("/reg_coeff_dict_keys(['", sa, "'])", sep = "")
how_many <- 10*1*8*1*50 # no. game iterations x no. genModels x no. TargetID x no. SensitiveAttribute x p_synth
N <- 10 # no. game iterations
trunc_levels <- c("1", paste(seq(5,20,5)), "26")



reading <- function(before_trunc, after_trunc, truncs, how_many, no_gameit = N){
  gi <- rep(1:no_gameit, each = how_many/no_gameit)
  results <- cbind( fread(paste0(before_trunc, truncs[1], after_trunc, ".csv", sep = ""), header = T), "trunc" = rep("1", how_many), "gameIt" = gi)
  
  for (i in truncs[2:(length(truncs)-1)]){
    results <- rbind(results, cbind( fread(paste0(before_trunc, i, after_trunc, ".csv", sep = ""), header = T), "trunc" = rep(paste(i), how_many), "gameIt" = gi))
  }
  
  results = rbind(results, cbind( fread(paste0(before_trunc, truncs[length(truncs)], after_trunc, ".csv", sep = ""), header = T), "trunc" = rep("none", how_many), "gameIt" = gi))
  return(results)
}
```

```{r}
betas <- reading(before_trunc = before_trunc, after_trunc = after_trunc, truncs = trunc_levels, how_many = how_many, no_gameit = N)
```

```{r}
# prepare data for plotting

factors = c("sa", "gameIt")
betas[ , (factors) := lapply(.SD, factor, ordered = T), .SDcols = factors]
rm(factors)
betas[ , trunc := factor(trunc, levels = c("1", paste(seq(5,20,5)), "none"), ordered = T)]

# remove intercept
betas[, ':='(b0 = NULL, genModel = NULL, sa = NULL, tid = NULL)]

betas_long <- melt(betas, id.vars = c('trunc', 'gameIt'))

MAB <- betas_long[, mean(abs(value)), by = .(trunc, gameIt)]
med <- MAB[, .(median(V1)), by = .(trunc)]
WCAB <- betas_long[, max(abs(value)), by = .(trunc)]
```


```{r}
# plotting parameters
mbcomp <- 0.5
mbCvine <- 0.5
xPB <- TeX(r'($\epsilon$)')
xCvine <- "truncation level"
axisCTTV <- element_text(size=20)
axisCPB <- element_text(size=30)
ytext <- TeX(r'($MAB_{totcst}$)') 
ytext_WC <- TeX(r'($WCAB_{totcst}$)')
tm <- 0.5




# MAB plot
ggplot(MAB, aes(x = trunc, y = V1)) +
  labs(x =xCvine, y = ytext) +
  guides(colour = "none") +
  theme_minimal() +
  theme(text = element_text(size = 30), legend.position = "left",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = axisCPB,
        axis.text.y = element_text(size=30),
        legend.text = element_text(size = 30),
        plot.margin=unit(c(tm,0,mbCvine,0), 'cm')
  ) +
  geom_boxplot(aes(y = V1, group = trunc), width = 0.5, fill = '#0099FF', size = 1, position=position_dodge(0.6), alpha = 0.8) +
  geom_path(data = med, aes(x = trunc, y = V1, group = 1), linewidth = 1) +
  scale_x_discrete(labels = c("1", paste(seq(5,20,5)), 'no')) +
  scale_y_continuous(breaks = seq(from = 0.04, to = 0.1, by = 0.02), limits = c(0.03, 0.1)) +
  panel_border()

# WCAB plot
ggplot(WCAB, aes(x = trunc, y = V1)) +
  labs(x =xCvine, y = ytext_WC) +
  guides(colour = "none") +
  theme_minimal() +
  theme(text = element_text(size = 30), legend.position = "left",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = axisCPB,
        axis.text.y = element_text(size=30),
        legend.text = element_text(size = 30),
        plot.margin=unit(c(tm,0,mbCvine,0), 'cm')
  ) +
  geom_path(group = 1, linewidth = 1) +
  geom_point(size = 7, color = '#0099FF') +
  scale_x_discrete(labels = c("1", paste(seq(5,20,5)), 'no')) +
  scale_y_continuous(breaks = seq(from = 0.4, to = 1.4, by = 0.2), limits = c(0.35, 1.42)) +
  panel_border()

```


# PRIVACY-UTILITY
## Privacy-Utility Plot
```{r}
# df for plotting
dfCvine <- as.data.frame(matrix(, nrow = length(trunc_levels), ncol = 3))
colnames(dfCvine) <- c("utility", "privAIA", "model")

# rearranging and summarizing utility results
resultsCvine <- resultsCvine %>% as.data.table()
resultsCvine[, trunc := factor(trunc, levels = paste(c(1, seq(5,20,5), 26)), ordered = T)]

subdf <- resultsCvine[resultsCvine$model == "Cvine",]
med <- summaryBy(AUC_synth ~ (trunc), data = subdf, FUN = list(median)) %>% as.data.frame()

# utility results to plotting df
dfCvine$utility <- med$AUC_synth.median
dfCvine$model <- paste0("Cvine_", med$trunc, sep = "")

# AIA results to plotting df
med <- MAB[, .(median(V1)), by = .(trunc)]
dfCvine$privAIA <- med$V1


dfCvine$utility <- dfCvine$utility %>% as.numeric()
dfCvine$privAIA <- dfCvine$privAIA %>% as.numeric()
dfCvine$model <- factor(dfCvine$model, ordered = T, levels = unique(dfCvine$model) )

# leave out un-truncated vine as last tree should not be included
dfCvine <- dfCvine[-6, ]

# colors per model in plot
color_palette_cvine <- c(brewer.pal(7, "Blues")[3:7])
desired_model_order <- c(unique(dfCvine$model))



ggplot(data = dfCvine, aes(x=utility, y=privAIA, color = factor(model, ordered = T))) +
  geom_point(size = 5) +
  geom_path(group=1, color = "grey", size = 1) +
  scale_y_continuous(breaks = seq(from = 0.04, to = 0.08, by = 0.01), limits = c(0.039, 0.081)) +
  scale_x_continuous(breaks = seq(from = 0.66, to = 0.69, by = 0.01), limits = c(0.66, 0.694)) +
  # scale_color_manual(values = color_palette_cvine) +
  theme_minimal() +
  panel_border() +
  scale_color_manual(values = color_palette_cvine, limits = unique(dfCvine$model), labels = c( paste0( "Cvine trunc ", c(1,seq(5,20,5))), "Cvine no trunc")) +
  labs(x = "utility (AUC)", y = "AIA privacy (MAB)", color = "Model:") +
  # guides(colour = "none") +
  theme_minimal() +
  theme(text = element_text(size = 30), legend.position = "left",
        legend.box = "vertical", plot.caption = element_text(hjust = 0),
        axis.text.x = element_text(size=30),
        axis.text.y = element_text(size=30),
        legend.text = element_text(size = 30)) +
  panel_border()
  

```